---
title: "利用常用分类算法对 Titanic 数据进行分类预测"
author: "Zhefeng Wang"
date: "May 27, 2015"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **[Kaggle Contest: Predicting Survival on the Titanic](https://www.kaggle.com/c/titanic)**

# **Content:**

**1.问题描述及理解**

**2.数据描述及理解**

**3.模型的选择及模型对数据的要求(模型假设)**

* **LDA QDA**
* **Logistic Regression**
* **KNN**
* **C4.5**
* **CART**
* **SVM**
* **Naive Bayes**
* **Bagging**
* **AdaBoost**
* **GBM**
* **Xgboost**
* **Random Forest**
* **EM**
* **Kmeans**
* **Apriori**
* **PageRank**
* ...

**4.根据模型的限制对数据进行预处理**

* **把变量分类**
* **探索性数据分析**
    + **描述性分析**
    + **可视化分析**
* **数据变换**
    + **Skewness Transformation** e1071::skewness() hist() lattice::histogram, caret::BoxCoxTrans() %>% predict(), MASS::boxcox() preProcess() %>% predict()...
    + **Centering and Scaling** Scale(), caret::preProces() %>% predict()...
* **缺失值处理missing value : impute**
    + impute::impute.knn(), preProcess() %>% predict
* **特征提取Feature extraction : PCA**
    + prcomp() need to center and scale, preProcess() %>% predict()
* **异常值处理Outlier : Spatial Sign** 
    + spatialSign(), preProcess() %>% predict()
* **过滤filter for near-zero variance predictors**
    + caret::nearZeroVar()
* **filter on between-predictor correlations** 
    + cor() corrplot::corrplot(), caret::findCorrelayions(), subselect
* **构造哑变量 Create Dummy Variable** 
    + caret::dummyVars() %>% predict()
* **Feature Selection**
* **数据集分割 Data Split** 
    + caret::createDataPartition()
* **...**

**5.建立预测模型**

* **模型调节(Model Tuning) -- 模型的Tuning Parameter，避免Overfitting**
* **数据重抽样方法(Data Split) -- Bootstrap CV,估计出模型表现的平均结果**
* **模型评估(Model Evaluation) -- 模型表现好坏的准则，选择出Optional Tuning Parameter**
* **模型选择(Model Selection) -- 根据选出的最优调节参数，选择出Final MOdel**

**6.利用建立的最终模型(Final Model)对测试数据(Test)进行预测并产生提交结果(my_solution)**

**7.总结** 

* **优点**
* **不足**


# **1.问题描述及理解**

## **From Kaggle's competition details:**

> **Description**: 
> The sinking of the RMS Titanic is one of the most infamous shipwrecks in history. On April 15, 1912, during her maiden voyage, the Titanic sank after colliding with an iceberg, killing 1502 out of 2224 passengers and crew. This sensational tragedy shocked the international community and led to better safety regulations for ships.*One of the reasons that the shipwreck led to such loss of life was that there were not enough lifeboats for the passengers and crew*. Although there was some element of luck involved in surviving the sinking, some groups of people were more likely to survive than others, such as *women*, *children*, and *the upper-class*.

> **Objective**:
> Apply the tools of machine learning to predict which passengers survived the tragedy.

> **[Data](https://www.kaggle.com/c/titanic/data)**

# **2.数据描述及理解**

## **Variable Description:**

variable name  | description
-------------- | -----------------------------------------------
Survived       | Survival (0 = No; 1 = Yes)  
Pclass         | Passenger Class (1 = 1st; 2 = 2nd; 3 = 3rd)  
Name           | Name  
Sex            | Sex  
Age            | Age  
SibSp          | Number of Siblings/Spouses Aboard  
Parch          | Number of Parents/Children Aboard  
Ticket         | Ticket Number  
Fare           | Passenger Fare  
Cabin          | Cabin  
Embarked       | Port of Embarkation (C = Cherbourg; Q = Queenstown; S = Southampton)  

## **Special Note:**  

* **Pclass** is a proxy for socio-economic status (SES) [1st ~ Upper; 2nd ~ Middle; 3rd ~ Lower]  
* **Age** is in Years; Fractional if Age less than One (1) If the Age is Estimated, it is in the form xx.5 
* With respect to the family relation variables (i.e. sibsp and parch) some relations were ignored. The following are the definitions used for sibsp and parch :  
    + **Sibling**:  Brother, Sister, Stepbrother, or Stepsister of Passenger Aboard Titanic  
    + **Spouse**:   Husband or Wife of Passenger Aboard Titanic (Mistresses and Fiances Ignored)  
    + **Parent**:   Mother or Father of Passenger Aboard Titanic  
    + **Child**:    Son, Daughter, Stepson, or Stepdaughter of Passenger Aboard Titanic  
    
    + Other family relatives excluded from this study include cousins,  nephews/nieces, aunts/uncles, and in-laws.  Some children travelled only with a nanny, therefore parch=0 for them.  As well, some travelled with very close friends or neighbors in a village, however, the definitions do not support such relations. 
    
## **载入全局用到的包**

```
library(printr)
```

```{r, message = FALSE, background = '#F7F7F7', highlight=TRUE, comment='##', results='markup', tidy=TRUE}
library(caret)
library(ggplot2)
library(dplyr)
```

## **读取数据**

```{r, background = '#F7F7F7', highlight=TRUE, comment='##', results='markup', tidy=TRUE}
## Method 1  
setwd("D:/My Directory/DM/Titanic/data")
train = read.csv("train.csv", na.strings = c('NA', ''), stringsAsFactors = F)
test = read.csv("test.csv", na.strings = c('NA', ''), stringsAsFactors = F)
## Method 2
train = read.csv(url("http://s3.amazonaws.com/assets.datacamp.com/course/Kaggle/train.csv"),
                 na.strings = c("NA", ""))
test = read.csv(url("http://s3.amazonaws.com/assets.datacamp.com/course/Kaggle/test.csv"),
                na.strings = c("NA", ""))
```

## **查看数据集状态**

```{r, background = '#F7F7F7', highlight=TRUE, comment='##', results='markup', tidy=TRUE}
train = tbl_df(train)
train
str(train)
head(train)
sapply(train, class)
sapply(train, function(x) sum(is.na(x)))
str(test)
sapply(test, class)
sapply(test, function(x) sum(is.na(x)))
```

# **3.模型的选择及模型对数据的要求(模型假设)**













# **4.根据模型的限制对数据进行预处理**

## **(0)把变量分类**

```{r}
numTrainPredictor = train[, c(6, 10)]

facTrainPredictor = train[, -c(6, 10)]

Response = train[, 2]
```




## **(1)探索性数据分析/Understanding data**
### **(i)描述性统计分析**

```{r}
summary(mutate(train, PassengerId = NULL))
Hmisc::describe(mutate(train, PassengerId = NULL))
```

### **(ii)数据可视化分析**


没有进行可视化的变量  | 变量类型    
--------------------- | ---------- 
PassengerId           | 乘客序列号 
Name                  | 名字       
Ticket                | 船票编号   
Cabin                 | 船舱编号   


进行可视化的变量 | 变量类型   | 图形 
-------------------- | ---------- | ------
Survived             | 类别型     | 条形图
Pclass               | 类别型     | 条形图
Sex                  | 类别型     | 条形图
SibSp                | 类别型     | 条形图
Parch                | 类别型     | 条形图
Embarked             | 类别型     | 条形图
Age                  | 数值型     | 直方图
Fare                 | 数值型     | 直方图




#### **Survived**

```{r}
table(train$Survived)
```

##### **Method 1**

```{r}
barplot(table(train$Survived), 
        names.arg = c("Perished", "Survived"),
        main="Survived (passenger fate)", col="black")
```

##### **Method 2**

```{r}
ggplot(data = train, aes(x = factor(Survived), fill = factor(Survived))) + 
    geom_bar() + 
    ggtitle("Survived (passenger fate)") + 
    xlab("Survived") + 
    theme_bw()
```


#### **Pclass**

```{r}
table(train$Pclass)
```

##### **Method 1**

```{r}
barplot(table(train$Pclass), 
        names.arg = c("first", "second", "third"),
        main = "Pclass (passenger traveling class)", col = "firebrick")
```

##### **Method 2**

```{r}
ggplot(data = train, aes(x = factor(Pclass), fill = factor(Pclass))) + 
    geom_bar() + 
    ggtitle("Pclass (passenger traveling class)") + 
    xlab("Pclass") + 
    theme_bw()
```



```{r}
table(train$Survived, train$Pclass)
ggplot(data = train, aes(x = factor(Pclass))) + 
    geom_bar() + 
    facet_grid(. ~ Survived) + 
    ggtitle("Passenger survived or not at each Pclass") + 
    xlab("Pclass") + 
    ylab("Passenger Count") + 
    theme_bw()
ggplot(data = train, aes(x = factor(Survived))) + 
    geom_bar() + 
    facet_grid(. ~ Pclass) + 
    ggtitle("Passenger survived or not at each Pclass") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
ggplot(data = train, aes(x = factor(Survived), fill = factor(Pclass))) + 
    geom_bar() + 
    ggtitle("Passenger survived or not at each Pclass") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
ggplot(data = train, aes(x = factor(Pclass), fill = factor(Survived))) + 
    geom_bar() + 
    ggtitle("Passenger survived or not at each Pclass") + 
    xlab("Pclass") + 
    ylab("Passenger Count") + 
    theme_bw()
```

#### **Sex**

```{r}
table(train$Sex)
```

##### **Method 1**

```{r}
barplot(table(train$Sex), main="Sex (gender)", col="darkviolet")
```

##### **Method 2**
 
```{r}
ggplot(data = train, aes(x = factor(Sex), fill = factor(Sex))) + 
    geom_bar() + 
    ggtitle("Sex (gender)") + 
    xlab("Sex") + 
    theme_bw()
```


```{r}
table(train$Survived, train$Sex)
ggplot(data = train, aes(x = factor(Survived))) + 
    geom_bar() + 
    facet_grid(. ~ Sex) + 
    ggtitle("Passenger survuved or not in different Sex") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
ggplot(data = train, aes(x = factor(Survived), fill = factor(Sex))) + 
    geom_bar() + 
    ggtitle("Passenger survived or not in different Sex") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
```

#### **Age** 

```{r}
hist(train$Age, main="Age", xlab = NULL, col="brown")
ggplot(data = train, aes(x = Age)) + geom_histogram() + ggtitle("Age") + theme_bw()
```

#### **SibSp**

```{r}
table(train$SibSp)
```

##### **Method 1**

```{r}
barplot(table(train$SibSp), main="SibSp (siblings + spouse aboard)", col="darkblue")
```

##### **Method 2**

```{r}
ggplot(data = train, aes(x = factor(SibSp), fill = factor(SibSp))) + 
    geom_bar() + 
    ggtitle("SibSp (siblings + spouse aboard") + 
    xlab("SibSp") + 
    theme_bw()
```


```{r}
table(train$Survived, train$SibSp)
ggplot(data = train, aes(x = factor(Survived))) + 
    geom_bar() + 
    facet_grid(. ~ SibSp) + 
    ggtitle("Passenger survuved or not in different SibSp") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
ggplot(data = train, aes(x = factor(Survived), fill = factor(SibSp))) + 
    geom_bar() + 
    ggtitle("Passenger survived or not in different Sibsp") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
ggplot(data = train, aes(x = factor(SibSp), fill = factor(Survived))) + 
    geom_bar() + 
    ggtitle("Passenger survived or not in different Sibsp") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
```

#### **Pach**

```{r}
table(train$Parch)
barplot(table(train$Parch), main="Parch (parents + kids aboard)", col="gray50")
table(train$Survived, train$Parch)
ggplot(data = train, aes(x = factor(Survived))) + 
    geom_bar() + 
    facet_grid(. ~ Parch) + 
    ggtitle("Passenger survuved or not in different Parch") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
```

#### **Fare**
 
```{r}
hist(train$Fare, main="Fare (fee paid for ticket[s])", xlab = NULL, col="darkgreen")
```


#### **Embarked**

```{r}
table(train$Embarked)
barplot(table(train$Embarked), 
        names.arg = c("Cherbourg", "Queenstown", "Southampton"),
        main="Embarked (port of embarkation)", col="sienna")
table(train$Survived, train$Embarked)
ggplot(data = train, aes(x = factor(Survived))) + 
    geom_bar() + 
    facet_grid(. ~ Embarked) + 
    ggtitle("Passenger survuved or not in different Embarked") + 
    xlab("Survived") + 
    ylab("Passenger Count") + 
    theme_bw()
```


#### **(iii)数据变换**

### **(2)缺失值处理**

### <span class = 'red'>Missing variables : **Age**, **Fare**, **Cabin**, **Embarked**</span>

#### **All data, both training and test set:**

```{r}
test$Survived = NA
all_data = rbind(train, test)
sapply(all_data, function(x) sum(is.na(x)))
```

#### **缺失值可视化**

```{r}
library(Amelia)
missmap(all_data, main="Titanic Training Data - Missings Map", 
        col=c("yellow", "black"), legend=FALSE)
```

#### **Fill in missing Age values:**

```{r}
library(rpart)
predicted_age <- rpart(Age ~ Pclass + Sex + SibSp + Parch + Fare + Embarked,
                       data = all_data[!is.na(all_data$Age), ], method = "anova")
all_data$Age[is.na(all_data$Age)] <- predict(predicted_age, all_data[is.na(all_data$Age), ])
```



#### **Replace fare value of Passenger on row 1044 with the median fare value:**

```{r}
all_data$Fare[1044] <- median(all_data$Fare, na.rm = TRUE)
```

#### **Passenger on row 62 and 830 do not have a value for embarkment. Since many passengers embarked at Southampton, give them the value S and code all embarkment codes as factors.**

```{r}
all_data$Embarked[c(62,830)] = "S"
all_data$Embarked <- factor(all_data$Embarked)
```

#### **Delete the Cabin Name  Ticket Varables**

```{r}
all_data = all_data[, -c(11, 9, 4)]
```

#### **处理缺失值后的数据**

```{r}
sapply(all_data, function(x) sum(is.na(x)))
train = all_data[1:891, ]
test = all_data[892:1309, -2]
dim(train)
dim(test)
```

### **(3)Create dummary variables**

#### **method 1**

```{r}
dummies = dummyVars(Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked, 
                    data = train)
train2 =  predict(dummies, newdata = train)
train2 = as.data.frame(train2)
train2 = cbind(train[, 1:2], train2)
head(train2)
```

#### **method 2**

```{r}
dummies = model.matrix(Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked, data = train)
train3 = as.data.frame(dummies)
head(train3)
```

### **(4)Split training and testing data set**

#### **Training / testing data set**

```{r}
set.seed(123)
inTrain = sample(1:2, dim(train)[1], replace = TRUE, prob = c(0.8, 0.2))
training = train[inTrain == 1, ]
testing = train[inTrain == 2, ]
head(training)
dim(training)
dim(testing)

set.seed(123)
inTrain = createDataPartition(y = train$Survived, p = 0.8, list = FALSE)
training = train[inTrain, ]
testing = train[-inTrain, ]
head(training)
dim(training)
dim(testing)

set.seed(123)
inTrain = sample(1:2, dim(train2)[1], replace = TRUE, prob = c(0.8, 0.2))
training2 = train2[inTrain == 1, ]
testing2 = train2[inTrain == 2, ]
head(training2)
dim(training2)
dim(testing2)

set.seed(123)
inTrain = createDataPartition(y = train2$Survived, p = 0.8, list = FALSE)
training2 = train2[inTrain, ]
testing2 = train2[-inTrain, ]
head(training2)
dim(training2)
dim(testing2)
```

#### **5-folds CV**

```{r}
set.seed(123)
folds1 = createFolds(y = train$Survived, k = 5, list = FALSE, returnTrain = TRUE)
table(folds1)
sapply(folds1, length)
```

#### **repeat 5-folds cv**

```{r}
set.seed(123)
folds2 = createMultiFolds(y = train$Survived, k = 5, times = 3)
sapply(folds2, length)
```

#### **Bootstrap**

```{r}
set.seed(123)
resamples = createResample(y = train$Survived, times = 10, list = TRUE)
```


# **4.建立预测模型**

## **(1) Logistic Regression**

### **Training the model**
```{r}
logit.model = glm(Survived ~ ., data = training, family = "binomial")
summary(logit.model)
logit.response = predict(logit.model, testing, type = "response")
logit.predict = ifelse(logit.response > 0.5, "1", "0")
```

## Results

```{r}
### ConfusionMatrix
table(Predict = logit.predict, Survived = testing$Survived)
logit.accuracy = mean(logit.predict == testing$Survived)
logit.accuracy
```

```
# contrasts(Survived)
```

```{r}
confusionM = confusionMatrix(logit.predict, testing$Survived)
confusionM
```

```{r}
names(confusionM)
confusionM$positive
confusionM$table
confusionM$overall
confusionM$byClass
confusionM$dots
```



### ROC culer

```{r}
library(pROC)
logitROC = roc(testing$Survived, logit.response,
               levels = levels(as.factor(testing$Survived)))
plot(logitROC, type = "S", print.thres = 0.5)
```



# **5.利用建立的模型对测试数据进行预测并产生提交结果**

# **6.总结**

